---
title: "disfluencyStats_APR18"
author: "Emer Gilmartin"
date: "Apr 18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
# Background #

Create a database of Conversation A including disfluency labels.


## Definitions ##



## Research Questions ##


# Dataset #
First, set working directory to CC_DATA_SEPT/disfluency


```{r}
getwd()

setwd("/Users/emergilmartin/Dropbox/PHD_final/CASUAL_EG_KL_JE_2016/CC_DATA_EG_KL_0616/CC_DATA_SEPT/DYSA18")


getwd()
```

### Make dataframe ###
Make data frame for conversation from text file - each line is an interval from Praat TG and contains 4 comma separated values

* Start time
* tier
* label
* Stop time

There are three classes of tier

* Speaker - lower case letter denotes speaker - these are unique for each speaker in each conversation (although there are cases where the same speaker appears in different corpora)
* Overlap - each interval is coded with who was speaking/laughing during the interval e.g. a{LG}b{SP} means participant a was speaking and b was laughing at the time, {GS} means nobody was speaking. Overlap tier was generated using a Praat script adapted from José Joaquín Atria (Get ref). NB: In this version, silence is defined as the absence of any vocalisation - so laughter is counted as non-silence for overlap silence purposes.
* Phase - each interval is coded with indicator of chat(o) or chunk(x) plus type of chunk (not very accurate), and an indicator of chunk owner expressed as speaker letter

First, read in disfluency text file 
```{r}
dys <- read.csv("dys_final_F19.csv",header=F,sep=',',stringsAsFactors = F)

```

Set column names
```{r}
names(dys)<- c("tmin","tier","label","tmax","dft","dfnoip")


summary(dys)
```

add dur (duration) column
```{r}

dys$dur <- dys$tmax - dys$tmin
```

Make new labels column label2 which has x or o for phases in place of longer labels and same labels for everything else

First, make label2 same as label

```{r}
dys$label2 <- dys$label
summary(dys)
```

Next, create function to change phase labels to x or o in label2

```{r}
xo_lab <- function(df) {
    # df is a dataframe - want to get first character of "phases" label and insert into label2 column
    
    l1 <- length(df$label)
    
    for (i in 1:l1) {
        oldlab <- df$label[i]
       
        if (df$tier[i] == "phases") {
            df$label2[i] <- substring(oldlab,1,1)
           
            
        }
    }
    return(df)
    
}
```

apply to dys to make dys2

```{r}
dys2 <- xo_lab(dys)
head(dys2,10)
head(dys2$label2[dys2$tier == "phases"])

```

Now we want to make new columns with distance from start of each interval in df to 'containing' or 'including' phase. Will use  get_nl
### Function to get distance for tmin of each line to the tmin and tmax of 'including' phenomenon ###

This function takes a dataframe and a tier name phenoB (e.g. topic or bout)
Adds new columns - dlast, dnext, phenoB
It then finds which interval on the phenoB tier contains the start of each item  in df, so for each line in df it could find which bout the phenomenon starts in.
It adds the label name to phenoB, the distance from start of phenoB to start of item, and the distance from the start of item to the end of phenoB

```{r}
get_nl <- function(df, phenoB) {
    # df is a dataframe, phenoB is the name of the tier to be used as reference
    #first make new columns in df for distance from last and distance to next amd topic name
    
    df$dlast <- NA
    df$dnext <- NA
    df$t_name <- NA
    y <-head(df)
    print(y)
    
    # now make dataframe of phenoB 
    phenoB_slice <- df[df$tier == phenoB,]
    print(head(phenoB_slice))
    
    for (i in seq_along(df$tmin)) {
        for (j in seq_along(phenoB_slice$tmin)) {
            # for each line in phenoB_slice
            if ((phenoB_slice$tmin[j] <= df$tmin[i]) & (df$tmin[i] < phenoB_slice$tmax[j])) {
                # print("in loop 2")
                # print(phenoB_slice$label[j])
                df$dlast[i] <- df$tmin[i] - phenoB_slice$tmin[j]
                df$dnext[i] <- phenoB_slice$tmax[j] - df$tmin[i]
                df$t_name[i] <- phenoB_slice$label[j]
                # print(df[i,])
            }
        }
    }
    return(df)
    
}
```

get_nl on dys2

```{r}

dys_Nl <- get_nl(dys2,"phases")


#run summary on new df and original for sanity check
summary(dys_Nl)
summary(dys)
```

Find out for chunks who is owner of chunk
Create function get_own which looks at t_name, if it begins with 'o', then owner is everyone, if it begins with x, then owner is speaker of chunk
 and also creates chatchunk column with x or o 

``` {r}
get_own <- function(df) {
    # df is a dataframe - 
    # create owner tier with NA, get first character of t_name tier - if "o", df$owner is "everyone", if "x", df$owner is 5th character of t_name
    
    df[,"owner"] <- NA
    df[,"chatchunk"] <- NA
    
    l1 <- length(df$t_name)
    
    for (i in 1:l1) {
        
        t_name1 <- df$t_name[i]
        type_1 <- substring(t_name1,1,1)
        
        
        if (type_1 == "o") {
            df$owner[i] <- "everyone"
            df$chatchunk[i] <- "o"
            
            
        }else if (type_1 == "x") {
            df$owner[i] <- substring(df$t_name[i],5,5)
            df$chatchunk[i] <- "x"
        }
    }
    return(df)
    
}
```

add owner and chatchunk column

``` {r}

df_all <- get_own(dys_Nl)
head(df_all, 30)
tail(df_all,30)

```

## Add gender columns for speaker and for chunk owner

```{r}
df_all$spgen <- rep('none', length(df_all$tier))
fem <- c('a','e','g','k','o','p','q','t','u','x','y')
mas <- c('b','c','d','f','h','j','l','m','n','r','s','v','w')

for (i in 1:length(df_all$spgen)) {
    if (df_all$tier[i] %in% fem)
    {df_all$spgen[i] <- 'f'
    } else if (df_all$tier[i] %in% mas)
    { df_all$spgen[i] <- 'm'
    }
}

df_all$chgen <- rep('none',length(df_all$owner))
for (i in 1:length(df_all$chgen)) {
    if (df_all$owner[i] %in% fem)
    {df_all$chgen[i] <- 'f'
    } else if (df_all$owner[i] %in% mas)
    { df_all$chgen[i] <- 'm'
    }
}

head(df_all)
table(df_all$spgen)
table(df_all$chgen)
table(df_all$chatchunk)


```


add labelf, factorized version of label column
```{r}
df_all$labelf<-as.factor(df_all$label)
summary(df_all)
```

## Final Dataset and variables

factorize some variables and summarise final df and get list of columns in df_all

```{r}
# factorize owner, chatchunk,spgen, chgen 
df_all$owner <- as.factor(df_all$owner)
df_all$chatchunk <- as.factor(df_all$chatchunk)
df_all$spgen <- as.factor(df_all$spgen)
df_all$chgen <- as.factor(df_all$chgen)

# # add chl - length of phase where label falls
# for (i in 1:length(df_all$dur)) {
#     nowch <- df_all$t_name[i]
#     chlen <- df_all$dur[df_all$label==nowch]
#     df_all$chl[i] <-chlen
# }

# add new column with type of tier -- speech, sipu, phone, word, df

table(df_all$tier)

df_all$typet <-  df_all$tier
df_all$speaker <- df_all$tier

for (i in 1:length(df_all$tier)) {
    if (substring(df_all$tier[i],2,2)=='_') {
        df_all$typet[i] <- substring(df_all$tier[i],3)
        df_all$speaker[i] <- substring(df_all$tier[i],1,1)
    }else if (df_all$tier[i] %in% c('a','b','c','d','e')) {
        df_all$typet[i] <- 'speech'
        df_all$speaker[i] <- df_all$tier[i]
        }
}

table(df_all$typet)
table(df_all$speaker)

# make variable chisp - true if speaker is chunk owner, else false

df_all$chisp<- df_all$speaker==as.character(df_all$owner)
summary(df_all)
names(df_all)
```


Variable | Type | Description
---------|----- | -----------------------
tmin     | num  | Start time for interval
---------|----- | -----------------------
tier | char | Praat tier interval came from - a,b, c.. for speakers, overlap, or phases (renamed to phases in txt file from chunks in Praat)
---------|----- | -----------------------
label | char | label of Praat interval - for speakers ({SP}, {SL}, {LG}), for overlap code of who and what is present in overlap or {GS} for global silence, for phases(chunks) code for chat or chunk beginning with o or x and with 5th character in chunk labels denoting owner of chunk
---------|----- | -----------------------
tmax | num | end time for interval
---------|----- | -----------------------
dft | char | disfluency type
---------|----- | -----------------------
tierf | factor | tier factorized
---------|----- | -----------------------
dur | num | duration of interval
---------|----- | -----------------------
label2 | char | same as label but has "x" or "o" instead of full chat or chunk labels
---------|----- | -----------------------
labelf | factor | same as label but has "x" or "o" instead of full chat or chunk labels and is factorised
---------|----- | -----------------------
dlast | num | distance from beginning of enclosing phase - result of running get_nl(phases) on each conversation subsetted from df - maybe add line to get_nl so it gives more info on which phenomenon it's been run on
---------|----- | -----------------------
dnext | num | distance from end of enclosing phase 
---------|----- | -----------------------
t_name | char | name of chunk or chat
---------|----- | -----------------------
owner | factor | generated using get_owner function from t_name - owner of chunk in which interval falls
---------|----- | -----------------------
speaker | char | what speaker tier interval comes from
---------|----- | -----------------------
chisp | char | logical - true if speaker is the same as owner
---------|----- | -----------------------
spgen | factor | gender of speaker (when tier is a speaker), else none
---------|----- | -----------------------
chgen | factor | gender of chunk owner
---------|----- | -----------------------
chatchunk | factor | whether part of chat or chunk
---------|----- | -----------------------
chl       | num | length of phase where label falls
---------|----- | -----------------------

# EXPORT FINAL DATASET  - use saveRDS so it can be loaded under a different name

```{r}
write.csv(df_all, "dys2_df.csv", row.names=FALSE)
saveRDS(df_all, "dys2_df.Rda")
```

