---
title: "overlap"
author: "Emer Gilmartin"
date: "17/2/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(knitr)

library(plyr)
library(dplyr)

opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(moments)
```

# Introduction ###

This uses the database created in CC_MakeDB for statistics on silences and overlaps in dataset of 6 conversations.

# Dataset

First, set working directory to CC_DATA_SEPT


```{r}

setwd("/Users/emergilmartin/Dropbox/PHD_final/CASUAL_EG_KL_JE_2016/CC_DATA_EG_KL_0616/CC_DATA_SEPT")

```


Read in data frame produced by CC_MakeDB.Rmd


```{r}

ccdf <- readRDS("ccdf.RDA")

# check what variables are there

names(ccdf)

df_all <- ccdf
```

Create dataframe containing only labels from Praat overlap tiers in each conversation
```{r}

# make overlaps df

overlaps <- df_all[df_all$tier =='overlap',]

summary(overlaps$tier)

table(overlaps$tier)

# test labels - there were a few {SL} in the overlap labels which should not have been there. Checked back with Praat and found in ABCDEF_SOC
# Cleaned up ABCDEF_SOC to BESTENDtest.txt, which is now in MakeDB.RMD to generate corrected ccdf
# NEED TO FIX PRAAT AT SOME STAGE

# This is just a sanity test that the corrected version is being used

sl<- grep(pattern='SL', x=overlaps$label)
sl

```

Create new variables showing number of concurrent speakers in interval, nosp, and number of concurrent laughers, nolg, in overlaps

```{r}
overlaps$lablen <- nchar(overlaps$label)


# labels from Praat overlap tier have either 4 characters ({GS}) and are global silence 
# or have some multiple of 5 characters, with each 5 denoting a speaker and an activity (speech or laughter)
# a{SP}b{LG}c{SP} would indicate a and c are speaking and b is laughing and everyone else is silent

# create columns for number of speakers, nosp, and number of laughers, nolg,
# using regmatches to create vector of number of appearances of "SP" or "LG" in labels

# Number of speakers
overlaps$nosp <- lengths(regmatches(overlaps$label,gregexpr('SP',overlaps$label)))

# Number of laughers
overlaps$nolg <- lengths(regmatches(overlaps$label,gregexpr('LG',overlaps$label)))
```

# OVERALL SPEECH DISTRIBUTION

This shows the proportions of silence, single speaker speech, 2 person overlap, 3 person overlap, etc., for the corpus as a whole. It should be noted that laughter has been treated as silence for this preliminary analysis.
```{r}
table(overlaps$nosp)
tapply(overlaps$dur, overlaps$nosp,sum)
tapply(overlaps$dur, overlaps$nosp,sum)*100/sum(overlaps$dur)
barplot(tapply(overlaps$dur, overlaps$nosp,sum)*100/sum(overlaps$dur),col = c('red','yellow','blue','orange','white', 'pink'), legend=rownames(tapply(overlaps$dur, overlaps$nosp,sum)))

```

From the table it can be seen that silence accounts for 23.42% of conversational time, while single party speech accounts for 68.49%. Two speaker overlap is 7.6% while three party accounts for under 0.5%. Overlap involving more than three persons is very rare in the corpus, with .02% of total conversational time taken up by 4 party overlap (21 instances), while there is only one instance of 5 party overlap in the entire corpus.


# SPEECH DISTRIBUTION BY CONVERSATION

```{r}

table(overlaps$nosp,overlaps$conv)
# There is a problem when trying to use tapply and prop.table as there were zero values for 4 and 5 on some conversations which led to NAs in tables of duration by conversation and number speaking so prop.table would not work
# SOLUTION: do tapply and change NAs to zeros - THIINK ABOUT WHETHER THIS WOULD WORK WITH MEANS!!!

# myta is a function to do the above - take df and variable (df$xxx), tapply for duration against number of speakers/laughers and conversation
# and replace NAs with zeros. 
# output is table which can then be prop.tabled and barplotted

myta <- function(x,nowhat) {
    mytab <- tapply(x$dur,list(nowhat,x$conv),sum)
    mytab[is.na(mytab)]<-0
    
    return(mytab)
}

# Get table of total duration of speech by 0,1,2.. speakers per conversation with NAs replaced by zeros
myt<-myta(overlaps,overlaps$nosp)

myt

# Now get prop.table by row in percentages
prop.table(myt,2)*100
barplot(prop.table(myt,2)*100, main='No.of speakers by duration per conversation %', col = c('red','yellow','blue','orange','white', 'pink'),legend=rownames(myt))

#create dummy variable for graphs - to get 3 possibilities 0=2+, 1=1,2=0
overlaps$shnosp<-20

summary(overlaps$nosp)

table(overlaps$nosp)

for(i in 1:length(overlaps$dur)){
    if(overlaps$nosp[i]==0){
        overlaps$shnosp[i]<-2
    } else if(overlaps$nosp[i]==1){
        overlaps$shnosp[i]<-1
    }else {
        overlaps$shnosp[i]<-0
    }
}

table(overlaps$shnosp)

my2<-tapply(overlaps$dur,list(overlaps$shnosp,overlaps$conv),sum)

barplot(prop.table(my2,2)*100, main='No.of speakers by duration per conversation %')

pdf('ov_conv2.pdf', width=8, height = 5)
barplot(prop.table(my2,2)*100, main='No.of speakers by duration per conversation %')
dev.off()

```

# SPEECH DISTRIBUTION BY CONVERSATION OMITTING SILENCE

```{r}

# get df of speech numbers greater than 0 - so no silence
spnosil <- overlaps[overlaps$nosp != 0,]

table(spnosil$nosp)

table(spnosil$nosp, spnosil$conv)
tapply(spnosil$dur, spnosil$nosp,sum)*100/sum(spnosil$dur)

barplot(tapply(spnosil$dur, spnosil$nosp,sum)*100/sum(spnosil$dur), main='speech overlap distribution (omit silence) %', col = c('yellow','blue','orange','white', 'pink'), legend=rownames(tapply(spnosil$dur, spnosil$nosp,sum)))

sp<-myta(spnosil,spnosil$nosp)
sp

prop.table(sp,2)*100

barplot(prop.table(sp,2)*100, main='speech overlap distribution per conversation (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(sp))
```

# Speech Proportions in Chat vs Chunk

Proportion of overlap (0,1,2...) by chatchunk

```{r}
# Everything against chatchunk

table(overlaps$nosp,overlaps$chatchunk)



# Ammend myta to make mytach - over chunks rather than conversations

mytach <- function(x,nowhat) {
    mytab <- tapply(x$dur,list(nowhat,x$chatchunk),sum)
    mytab[is.na(mytab)]<-0
    
    return(mytab)
}

# sil,speech - overlaps, nosp

mytch <- mytach(overlaps,overlaps$nosp)

mytch

prop.table(mytch,2)*100

barplot(prop.table(mytch,2)*100, main='speech overlap distribution per chatchunk (inc silence) %', col = c('red','yellow','blue','orange','white','pink'), legend=rownames(mytch))

# speech no sil - spnosil, nosp

spch <- mytach(spnosil,spnosil$nosp)
spch

prop.table(spch,2)*100

barplot(prop.table(spch,2)*100, main='speech overlap distribution per chatchunk (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(spch))


# with shnosp so only speech silence overlap rather than all n

# sil,speech - overlaps, nosp

mytch <- mytach(overlaps,overlaps$shnosp)

mytch

prop.table(mytch,2)*100

pdf('spov_sxo2.pdf', width=8, height = 5)
par(mfrow=c(1,2))
barplot(prop.table(mytch,2)*100, main='Speech, Silence, Overlap (%)', col = c('black','gray40','gray80'),names=c('Chat','Chunk'))

# speech no sil - spnosil, nosp

spch <- mytach(spnosil,spnosil$shnosp)
spch

prop.table(spch,2)*100

barplot(prop.table(spch,2)*100, main='Speech, Overlap (%)', col = c('black','gray40','gray80'),names=c('Chat','hunk'))
dev.off()
par(mfrow=c(1,1))

```
# LOOK AT DISTANCE FROM OVERLAPS TO END OF CHAT CHUNNK

```{r}
# use spnosil
# histogram of distance from any overlap to end of chat or chunk
over2<-spnosil[spnosil$nosp>=2,]
summary(over2)
median(over2$dnext)
over2[over2$dnext == max(over2$dnext),]
summary(df_all$dur[df_all$tier=='phases'])

hist(df_all$dur[df_all$tier=='phases'], breaks=seq(0,300,by=5))

summary(over2$dnext)
hist(over2$dnext, breaks=seq(0,300,by=5))

summary(over2$dlast)
hist(over2$dlast, breaks=seq(0,300,by=5))

hist(log(df_all$dur[df_all$tier=='phases']))

hist(log(over2$dnext))

hist(log(over2$dlast))

par(mfrow=c(1,3))
boxplot(over2$dnext~over2$chatchunk)
hist(over2$dnext[over2$chatchunk=='o'])
hist(over2$dnext[over2$chatchunk=='x'])

# Proportional distance from next boundary

median(over2$dnext/over2$chl)

par(mfrow=c(1,2))
hist(over2$dnext/over2$chl)
boxplot(over2$dnext/over2$chl~over2$chatchunk)

wilcox.test(dnext/chl ~ chatchunk, data = over2)

```



# OVERALL LAUGHER DISTRIBUTION
```{r}
table(overlaps$nolg)
tapply(overlaps$dur, overlaps$nolg,sum)
tapply(overlaps$dur, overlaps$nolg,sum)*100/sum(overlaps$dur)
barplot(tapply(overlaps$dur, overlaps$nolg,sum)*100/sum(overlaps$dur),col = c('red','yellow','blue','orange','white', 'pink'), legend=rownames(tapply(overlaps$dur, overlaps$nolg,sum)))
```

# OVERALL DISTRIBUTION OF NUMBER OF LAUGHERS PER CONVERSATION
```{r}
# Now get table and proptable for proportional duration per number of laughers in each conversation
myu<- myta(overlaps, overlaps$nolg)

myu

prop.table(myu,2)*100


# plot results - barplot shows proportions of 0,1,2,3,... simultaneous speakers in each conversation
# NOTE: 0 is silence, 1 is single speaker, 2 is 2 speakers ...

# NEED TO SORT OUT LEGEND POSITIONING
# 
# par(mfrow=c(1,2))
# 
# barplot(prop.table(myt,2)*100, main='No.of speakers distribution per conversation %', col = c('red','yellow','blue','orange','white', 'pink'))
barplot(prop.table(myu,2)*100, main='number of laughers distribution per conversation %', col = c('red','yellow','blue','orange','white', 'pink'))
# 
#        
# par(mfrow=c(1,1))


```


# laughter distribution by conversation (omit silence)
```{r}
lgnosil <- overlaps[overlaps$nolg != 0,]

table(lgnosil$nolg)

table(lgnosil$nolg, lgnosil$conv)

barplot(tapply(lgnosil$dur, lgnosil$nolg,sum)*100/sum(lgnosil$dur),main='laughter overlap distribution (omit silence) %', col = c('yellow','blue','orange','white', 'pink'), legend=rownames(tapply(lgnosil$dur, lgnosil$nolg,sum)))

lg<- myta(lgnosil,lgnosil$nolg)
lg
prop.table(lg,2)*100

barplot(prop.table(lg,2)*100, main='laughter overlap distribution per conversation (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(lg))

# par(mfrow=c(1,2))
# barplot(prop.table(sp,2)*100, main='speech overlap distribution per conversation (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(sp))
# barplot(prop.table(lg,2)*100, main='laughter overlap distribution per conversation (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(lg))
# par(mfrow=c(1,1))



```



# LAUGHER PROPORTIONS IN CHAT VS CHUNK

```{r}

table(overlaps$nolg,overlaps$chatchunk)

myuch <- mytach(overlaps,overlaps$nolg)

myuch

prop.table(myuch,2)*100

barplot(prop.table(myuch,2)*100, main='laughter overlap distribution per chatchunk (inc silence) %', col = c('red','yellow','blue','orange','white','pink'),legend=rownames(myuch))


# laughter no sil - lgnosil, nolg

lgch<-mytach(lgnosil,lgnosil$nolg)
lgch

prop.table(lgch,2)*100

barplot(prop.table(lgch,2)*100, main='laughter overlap distribution per chatchunk (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(lgch))

par(mfrow=c(1,2))
barplot(prop.table(spch,2)*100, main='speech overlap distribution per chatchunk (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(spch))
barplot(prop.table(lgch,2)*100, main='laughter overlap distribution per chatchunk (omit silence) %', col = c('yellow','blue','orange','white','pink'),legend=rownames(lgch))
par(mfrow=c(1,1))

```

Now check per conversation

```{r}
overlapsA<-overlaps[overlaps$conv=='A',]

summary(overlapsA)

#speech overlap proportion including silences
mytchA <- mytach(overlapsA,overlapsA$nosp)

mytchA
 
propA<- prop.table(mytchA,2)*100

propA

barplot(propA, main='speech overlap distribution per chatchunk in A (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))

overlapsB<-overlaps[overlaps$conv=='B',]
mytchB <- mytach(overlapsB,overlapsB$nosp)

mytchB

propB<- prop.table(mytchB,2)*100
propB
 
barplot(propB, main='speech overlap distribution per chatchunk in B (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))

overlapsC<-overlaps[overlaps$conv=='C',]
mytchC <- mytach(overlapsC,overlapsC$nosp)

mytchC
 
propC<- prop.table(mytchC,2)*100
propC

barplot(propC, main='speech overlap distribution per chatchunk in C (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))
 
overlapsD<-overlaps[overlaps$conv=='D',]
mytchD <- mytach(overlapsD,overlapsD$nosp)
 
mytchD
 
propD<- prop.table(mytchD,2)*100
propD
 
barplot(propD, main='speech overlap distribution per chatchunk in D (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))
 
overlapsE<-overlaps[overlaps$conv=='E',]
mytchE <- mytach(overlapsE,overlapsE$nosp)

mytchE

propE<- prop.table(mytchE,2)*100
propE

barplot(propE, main='speech overlap distribution per chatchunk in E (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))

overlapsF<-overlaps[overlaps$conv=='F',]
mytchF <- mytach(overlapsF,overlapsF$nosp)

mytchF

propF<- prop.table(mytchF,2)*100
propF

barplot(propF, main='speech overlap distribution per chatchunk in F (inc silence) %', col = c('red','yellow','blue','orange','white','pink'))

# speech without silences

spnosilA <- spnosil[spnosil$conv=='A',]

spchA <- mytach(spnosilA,spnosilA$nosp)
spchA

prop.table(spchA,2)*100

barplot(prop.table(spchA,2)*100, main='speech overlap distribution per chatchunk in A (omit silence) %', col = c('yellow','blue','orange','white','pink'))


spnosilB <- spnosil[spnosil$conv=='B',]

spchB <- mytach(spnosilB,spnosilB$nosp)
spchB

prop.table(spchB,2)*100

barplot(prop.table(spchB,2)*100, main='speech overlap distribution per chatchunk in B (omit silence) %', col = c('yellow','blue','orange','white','pink'))

spnosilC <- spnosil[spnosil$conv=='C',]

spchC <- mytach(spnosilC,spnosilC$nosp)
spchC

prop.table(spchC,2)*100

barplot(prop.table(spchC,2)*100, main='speech overlap distribution per chatchunk in C (omit silence) %', col = c('yellow','blue','orange','white','pink'))

spnosilD <- spnosil[spnosil$conv=='D',]

spchD <- mytach(spnosilD,spnosilD$nosp)
spchD

prop.table(spchD,2)*100

barplot(prop.table(spchD,2)*100, main='speech overlap distribution per chatchunk in D (omit silence) %', col = c('yellow','blue','orange','white','pink'))

spnosilE <- spnosil[spnosil$conv=='E',]

spchE <- mytach(spnosilE,spnosilE$nosp)
spchE

prop.table(spchE,2)*100

barplot(prop.table(spchE,2)*100, main='speech overlap distribution per chatchunk in E (omit silence) %', col = c('yellow','blue','orange','white','pink'))

spnosilF <- spnosil[spnosil$conv=='F',]

spchF <- mytach(spnosilF,spnosilF$nosp)
spchF

prop.table(spchF,2)*100

barplot(prop.table(spchF,2)*100, main='speech overlap distribution per chatchunk in F (omit silence) %', col = c('yellow','blue','orange','white','pink'))


```
Get plots by conversation of only chunk and only chat - speech and silence

```{r}
# get df of only chunks

chukov <- overlaps[overlaps$chatchunk=='x',]

chov<- myta(chukov, chukov$nosp)

chov

prop.table(chov,2)*100

barplot(prop.table(chov,2)*100, main='silence and speech distribution in chunks per conversation %', col = c('red','yellow','blue','orange','white', 'pink'),legend=rownames(chov))

# get df of only chats

chatov <- overlaps[overlaps$chatchunk=='o',]

chav<- myta(chatov, chatov$nosp)

chav

prop.table(chav,2)*100

barplot(prop.table(chav,2)*100, main='silence and speech distribution in chat per conversation %', col = c('red','yellow','blue','orange','white', 'pink'),legend=rownames(chav))


```


Get plots by conversation of only chunk and only chat - speech only

```{r}
# get df omitting silence in chunks

chusp <- chukov[chukov$nosp !=0,]

chunksp<- myta(chusp, chusp$nosp)

chunksp

prop.table(chunksp,2)*100

barplot(prop.table(chunksp,2)*100, main='speech distribution in chunks per conversation %', col = c('yellow','blue','orange','white', 'pink'),legend=rownames(chunksp))

# get df of only chats

chasp <- chatov[chatov$nosp !=0,]

chatsp<- myta(chasp, chasp$nosp)

chatsp
prop.table(chatsp,2)*100

barplot(prop.table(chatsp,2)*100, main='speech distribution in chat per conversation %', col = c('yellow','blue','orange','white', 'pink'),legend=rownames(chatsp))
```


Laughter in chunks only or chat only side by side

Get plots by conversation of only chunk and only chat - laughter only

```{r}
# get df omitting silence in chunks
 
chulg <- chukov[chukov$nolg !=0,]

summary(chulg)
# 
chunklg<- myta(chulg, chulg$nolg)
# 
chunklg
# 
prop.table(chunklg,2)*100

barplot(prop.table(chunklg,2)*100, main='laughter distribution in chunks per conversation %', col = c('yellow','blue','orange','white', 'pink'),legend=rownames(chunklg))

# get df of only chats

chalg <- chatov[chatov$nolg !=0,]

chatlg<- myta(chalg, chalg$nolg)
 
chatlg
prop.table(chatlg,2)*100
 
barplot(prop.table(chatlg,2)*100, main='laughter distribution in chat per conversation %', col = c('yellow','blue','orange','white', 'pink'),legend=rownames(chatlg))
```
Look at mean proportion of silence per chunk vs mean proportion of silence per chat by duration - is there a significant difference?
Same for overlap - proportion of single speaker per chunk (as prop of total speech), same for 2 person overlap as prop of total overlap, etc.

EXPERIMENT - would myta work with means?

I would  worry that getting means where the value NA is replaced with 0 would make the number of values in divisor higher, thus making mean smaller
Check

```{r}

meanta <- function(x,nowhat) {
    mytab <- tapply(x$dur,list(nowhat,x$conv),mean)
    mytab[is.na(mytab)]<-0
    
    return(mytab)
}

meant<-meanta(overlaps,overlaps$nosp)

# with NAs still in

meantman<- tapply(overlaps$dur,list(overlaps$nosp,overlaps$conv),mean)

meant
meantman


prop.table(meant,2)*100

barplot(prop.table(meant,2)*100, main='speech overlap distribution means', col = c('yellow','blue','orange','white','pink'))
```

Todo

1. Get distribution of percentage speech, silence, overlap (nosp -= 1,0, >1) by chunk, chat
would involve tabling duration sums of speech, silence, laughter by chunk over total duration of each chunk 
write function to do this

```{r}



# make database of chat and chunk only

chdb <- df_all[df_all$tier =='phases',]
summary(chdb)

#loop through each chat or chunk and add value for sum of duration of silence, single speaker, 2+ speakers

for (i in 1:length(chdb$tier)) {
    thisch <- chdb$t_name[i]
    #get df of overlaps with this t_name
    thischdf <- overlaps[overlaps$t_name == thisch,]
    chdb$dur0[i] <- sum(thischdf$dur[thischdf$nosp==0])
    chdb$dur1[i] <- sum(thischdf$dur[thischdf$nosp==1])
    chdb$dur2p[i] <- sum(thischdf$dur[thischdf$nosp>1])
    chdb$dur2[i] <- chdb$dur0[i]+chdb$dur1[i]+chdb$dur2p[i]
}

summary(chdb)

# SILENCE PROPORTION
par(mfrow = c(1,3))
hist(chdb$dur0/chdb$dur2,col='red',xlim=c(0,.7),ylim=c(0,130))
abline(v=mean(chdb$dur0/chdb$dur2))
abline(v=median(chdb$dur0/chdb$dur2),col = "grey")

cho <-chdb[chdb$chatchunk=='o',]
hist(cho$dur0/cho$dur2,col='yellow',ylim=c(0,130),xlim=c(0,.7))
abline(v=mean(cho$dur0/cho$dur2))
abline(v=median(cho$dur0/cho$dur2),col = "grey")

chu <-chdb[chdb$chatchunk=='x',]
hist(chu$dur0/chu$dur2, col='blue',ylim=c(0,130),xlim=c(0,.7))
abline(v=mean(chu$dur0/chu$dur2))
abline(v=median(chu$dur0/chu$dur2),col = "grey")

hist(log(chdb$dur0/chdb$dur2),col='red')
hist(log(cho$dur1/cho$dur2),col='yellow')
hist(log(cho$dur2p/cho$dur2),col='blue')



par(mfrow=c(1,1))

boxplot(chdb$dur0/chdb$dur2~chdb$chatchunk)
wilcox.test(dur0/dur2~chatchunk, data = chdb)

# wilcox.test(dur0/dur2~chatchunk, data = chdb,paired=TRUE)

boxplot(chdb$dur1/chdb$dur2~chdb$chatchunk)
wilcox.test(dur1/dur2~chatchunk, data = chdb)

boxplot(chdb$dur2p/chdb$dur2~chdb$chatchunk)
wilcox.test(dur2p/dur2~chatchunk, data = chdb)

# SINGLE SPEAAKER PROPORTION
par(mfrow = c(1,3))
hist(chdb$dur1/chdb$dur2,col='red',xlim=c(0,1),ylim=c(0,130))
abline(v=mean(chdb$dur1/chdb$dur2))
abline(v=median(chdb$dur1/chdb$dur2),col = "grey")

cho <-chdb[chdb$chatchunk=='o',]
hist(cho$dur1/cho$dur2,col='yellow',ylim=c(0,130),xlim=c(0,1))
abline(v=mean(cho$dur1/cho$dur2))
abline(v=median(cho$dur1/cho$dur2),col = "grey")

chu <-chdb[chdb$chatchunk=='x',]
hist(chu$dur1/chu$dur2, col='blue',ylim=c(0,130),xlim=c(0,1))
abline(v=mean(chu$dur1/chu$dur2))
abline(v=median(chu$dur1/chu$dur2),col = "grey")

par(mfrow=c(1,1))


boxplot(chdb$dur1/chdb$dur2~chdb$chatchunk)
wilcox.test(dur1/dur2~chatchunk, data = chdb)

```

Laughter
    
    
```{r} 
#loop through each chat or chunk and add value for sum of duration of silence, single speaker, 2+ speakers
lchdb<-chdb

for (i in 1:length(lchdb$tier)) {
    lthisch <- lchdb$t_name[i]
    #get df of overlaps with this t_name
    lthischdf <- overlaps[overlaps$t_name == lthisch,]
    lchdb$dur0[i] <- sum(thischdf$dur[lthischdf$nolg==0])
    lchdb$dur1[i] <- sum(thischdf$dur[lthischdf$nolg==1])
    lchdb$dur2p[i] <- sum(thischdf$dur[lthischdf$nolg>1])
    lchdb$dur2[i] <- lchdb$dur0[i]+lchdb$dur1[i]+lchdb$dur2p[i]
    lchdb$durl[i] <- lchdb$dur1[i]+lchdb$dur2p[i]
}

summary(lchdb)

par(mfrow = c(1,3))
# all laughter proportion of all phases
hist((lchdb$dur1+lchdb$dur2p)/lchdb$dur2,col='red')

# all laughter proportion of chats
cholg <-lchdb[lchdb$chatchunk=='o',]
hist((cholg$dur1+cholg$dur2p)/cholg$dur2,col='yellow')

# all laughter as prop of chunks
chul <-lchdb[lchdb$chatchunk=='x',]
hist((chul$dur1+chul$dur2p)/chul$dur2, col='blue')

hist(log((lchdb$dur1+lchdb$dur2p)/lchdb$dur2),col='red')
hist(log((cholg$dur1+cholg$dur2p)/cholg$dur2),col='yellow')
hist(log((chul$dur1+chul$dur2p)/chul$dur2),col='blue')



par(mfrow=c(1,1))

boxplot(log(lchdb$dur1/lchdb$durl)~lchdb$chatchunk)
wilcox.test(log(dur1/durl)~chatchunk, data = lchdb)

# boxplot(lchdb$dur1/lchdb$dur2~lchdb$chatchunk)
# wilcox.test(dur0/dur2~chatchunk, data = lchdb)

# wilcox.test(dur0/dur2~chatchunk, data = lchdb,paired=TRUE)

boxplot(lchdb$dur1/lchdb$durl~lchdb$chatchunk)
wilcox.test(dur1/durl~chatchunk, data = lchdb)

boxplot(lchdb$dur1/lchdb$durl~lchdb$chatchunk)
wilcox.test(dur1/durl~chatchunk, data = lchdb)

# boxplot(lchdb$dur2p/lchdb$dur2~lchdb$chatchunk)
# wilcox.test(dur2p/dur2~chatchunk, data = lchdb)


```
